6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-19 paper.tex
Refs for the evaluation

\usepackage{url}
\usepackage{minted}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage[style=alphabetic, sorting=nyt]{biblatex}
\addbibresource{bibliography.bib}

@@

Application level metrics can be collected using StatsD. Applications can send metrics to a local StatsD instance via UDP, which adds very little performance overhead. This means that it is possible to heavily instrument the critical paths of an application except in extremely performance sensitive scenarios. Both of these tools aggregate this data and flush it to a backend Graphite instance at configurable intervals. Graphite provides extremely flexible data visualisation techniques, but requires some up front investment in time to produce meaningful results.

@@

      require "redis" # External RubyGem
      Redis.new.ping == "PONG" or fail "Redis isn't responding"
    end
  end
\end{minted}

@@

\begin{minted}[fontfamily=fi4]{bash}
  curl -s https://management-server/agent/install | sh
\end{minted}

@@

\subsection{Bundled Checks \& Extensibility}

@@

\subsection{REST}

@@

\subsection{Root}

@@

        This requirement was satisfied. The installation process was tested on each target platform, Linux (Both Ubuntu 13.04 and Red Hat Enterprise Linux 6) and Mac OS X. A single command as documented earlier provides this functionality on all target platforms.

@@

        Service specifications can be executed using the `check' and `start' commands.

@@

        The bundled set of checks are documented in~\ref{}, they have been tested using the suite of unit tests in the management agent.

@@

        The installation procedure, followed by the `setup', `pull' and `start' commands will start monitoring on any Linux server. The checks will run continuously according to the intervals specified.

@@

    The reliability of the tool has steadily improved due to the iterative, generally test driven development process. A number of issues were fixed in the actual testing phase, but these were generally minor issues which didn't affect the reliability of the tool directly. \ref{}

@@

        During testing, checks generally executed quickly. The system adds a negligible overhead compared to executing the checks directly, they are necessarily I/O bound and therefore difficult to optimize any further.

@@

        In the event of an error, the system takes no longer than the check TTL (+ 3 seconds) to recognise it, and dispatch an incident email. Delivery of emails and SMS messages is subject to the performance of third party services but is generally very quick. During testing, no incidents were missed and all alerts were recieved successfully.

@@

        Running the monitoring agent (with a typical set of 5-8 checks) consumes the following resources: CPU: 0.1\% RAM: 31.5 MB Disk: $<$ 5MB

@@

        The architectural components implemented were developed and tested in isolation. Two components use Ruby, one Clojure and one JS/HTML, the decision to decompose the system into these components is extensively discussed in \ref{}.

@@

        Best practices such as effective object decomposition, inheritance and composition are used where appropriate. The management API adheres to the typical MVC structure of a Ruby on Rails project. The evidence of this should be apparent from the code listing. \ref{}

@@

        As detailed in the \ref{} section, the management API provides an API conforming to REST principles, facilitating simple integration with other services or tools.

@@

        As detailed in the \ref{} section, the management API returns data in JSON format, a popular encoding format.

@@

@@

Developers commonly see infrastructure issues as being a problem for system administrators, when in reality they are well placed to help with its prevention. Providing a tool that developers are comfortable using was a key goal of the project and one that I feel was achieved.

After implementing the concept, I remain convinced that it is a solid approach to practically managing complex applications. A suite of tests could range from very low level port checks to high level integration checks testing real application features, making it suitable for all kinds of application. Providing the primitive tools needed to test arbitrary properties of a system remains a powerful idea. The disadvantage to this flexibility is that the burden of writing good test cases is placed upon the user, something which could be improved with a more sophisticated service discovery mechanism and more bundled plugins. This is an area which could be expected to improve through open source contributions. Additionally, I expect that test suites would evolve over time, as more edge cases and problems in production are experienced and therefore identified quickly in future.

@@

Conceptually, one of the main concerns I have is the duplication of knowledge between actual application configuration and the test suite needed to verify it. The same could be argued for software unit testing, but it seems that with the rise in popularity of tools of a declarative nature such as Chef and Puppet, there should be a way to remove some of this duplication.

One of the only concerns around the use of the tool stem from its requirement for a Ruby installation on production servers. This was difficult to work around, as Ruby is particularly well suited to the implementation of a DSL and has a huge amount of open source libraries which developers can use to write specifications. It is also very familiar to a number of my target test users. However, it may be useful to look into other tools such as Google's Go language, which is statically linked and has no runtime dependencies.

I hope that the concepts and implementation of this tool can be directly re-used and expanded upon in future by open source contributions or competing projects, I feel that there is still lots of room for improvement but believe that it will be realised in time with this approach.

>>>>

\usepackage{url}
\usepackage{minted}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage[style=alphabetic, sorting=nyt]{biblatex}
\addbibresource{bibliography.bib}

@@

\label{StatsD}
Application level metrics can be collected using StatsD. Applications can send metrics to a local StatsD instance via UDP, which adds very little performance overhead. This means that it is possible to heavily instrument the critical paths of an application except in extremely performance sensitive scenarios. Both of these tools aggregate this data and flush it to a backend Graphite instance at configurable intervals. Graphite provides extremely flexible data visualisation techniques, but requires some up front investment in time to produce meaningful results.

@@

      require "redis" # External RubyGem
      Redis.new.ping == "PONG" or fail "Redis is not responding"
    end
  end
\end{minted}

@@

\label{bashinstall}
\begin{minted}[fontfamily=fi4]{bash}
  curl -s https://management-server/agent/install | sh
\end{minted}

@@

\subsection{Bundled Checks \& Extensibility}
\label{bundledchecks}

@@

\subsection{REST}
\label{rest}

@@

\subsection{Root}
\label{json}

@@

        This requirement was satisfied. The installation process was tested on each target platform, Linux (Both Ubuntu 13.04 and Red Hat Enterprise Linux 6) and Mac OS X. A single command as documented in \autoref{bashinstall} provides this functionality on all target platforms.

@@

        Service specifications, such as the examples satisfying the previous requirement, can be executed using the `check' and `start' commands. When using the check command, output is similar to that seen in \ref{}.

        The service overview page displays the results of checks on started daemons \ref{}.

@@

        The bundled set of checks are documented in \autoref{bundledchecks}, they have been tested using the suite of unit tests in the management agent. These bundled checks can be used in any health check block, and are added to relevant components in the automatic service discovery process.

@@

        The installation procedure, followed by the `setup', `pull' and `start' commands will start monitoring on any Linux server. The checks will run continuously according to the intervals specified. This can be observed from the management interface.

@@

    The reliability of the tool has steadily improved due to the iterative, generally test driven development process. A number of issues were fixed in the actual testing phase, but these were generally minor issues which did not affect the reliability of the tool directly. \ref{}

@@

        It was confirmed during testing, that the system adds a negligible overhead compared to executing the checks directly, they are necessarily I/O bound and therefore difficult to optimize any further.

@@

        In the event of a component failure, the system takes no longer than the configured check interval (+3 seconds) to recognise it, and dispatch an incident email. This is commonly around 15 seconds in total.

        If the management agent itself terminates unexpectedly, this will be detected at 3x the shortest configured check interval for that service. In concrete terms, this is generally around 30 seconds.

        Delivery of emails and SMS messages is subject to the performance of third party services but is generally very quick, at around 5-10 seconds.

        During testing, no incidents were missed and all alerts were recieved successfully.

@@

        Running the monitoring agent (with a typical set of 5-8 checks) consumes the following resources:

        \begin{table}[htbp]
          \centering
        \begin{tabular}{|r|l|}
          CPU & 0.1\% \\
          RAM & 31.5 MB \\
          Disk & $<$ 5MB \\
        \end{tabular}
        \end{table}

@@

        The architectural components implemented were developed and tested in isolation. Two components use Ruby, one Clojure and one JS/HTML, the decision to decompose the system into these components is extensively discussed in \autoref{section:architecture}.

@@

        Best practices such as effective object decomposition, inheritance and composition are used where appropriate. As the most complex component, the Management API adheres to the typical MVC structure of a Ruby on Rails project. The evidence of this should be apparent from the code listing.

@@

        As detailed in \autoref{rest}, the management API provides an API conforming to REST principles, facilitating simple integration with other services or tools.

@@

        As detailed in \autoref{json}, the management API returns data in JSON format, a popular serialisation format.

@@

\subsection{Critical Evaluation}

As evident from the previous subsections, the system delivered at least partially satisfied every requirement set out in the analysis phase. The tool is practically usable and deployed on a number of real systems. There are however a few weaknesses or areas of improvement upon the final implementation:

\begin{description}
  \item[Dependency on Ruby] For good reason, many of the target users of the tool are reluctant to install Ruby on production servers where it is not otherwise required. As previously discussed, the tool will manage this install process itself, reducing administrative burden, but it is still an unavoidable dependency which makes the footprint of the tool larger than necessary, and can sometimes make the installation process slow.

    Ideally, the management agent should be re-written in portable and dependency-free language such as Google's Go language, which compiles to a single binary with packaged dependencies. The reason this approach was not chosen from the beginning was the wealth of open source libraries (RubyGems) that could be used by developers in checks, as well as Ruby's meta-programming features and syntactic flexibility used to construct DSL's.

  \item[Passive Checks] The only supported method of asserting properties is via scheduled execution of tests. Considering the significant amount of infrastructure implemented to efficiently transport event data, applications could report health metrics as part of their normal execution. This approach is similar to the StatsD tool covered in \autoref{StatsD}. This could be especially useful where check overhead is a concern, or where properties are not observable from a `black box' perspective of the system under test.

    The omission of this feature is not considered significant weakness, as the vast majority of properties can be checked via the service specification. If subsequently implemented, it would only require implementation at the management agent level, the rest of the infrastructure would support this feature without modification.

  \item[Better Graphite Integration] Whilst not entirely within the scope of this project, it could be beneficial to display metrics such as application response times, average CPU load etc.\ as graphs retrieved from Graphite, this may help to resolve problems in sub-systems that do not have adequate `check coverage'. It would provide a greater granularity of feedback than currently provided, which may also help to anticipate problems before they actually affect users.
\end{description}

@@

Developers commonly see infrastructure issues as being a problem for system administrators, when in reality they are well placed to help with their prevention. Creating a tool that developers are comfortable using was a key goal of the project and one that I feel was achieved.

After implementing the concept, I remain convinced that it is a solid approach to practically managing complex applications. A suite of tests could range from very low level port checks to high level integration checks testing real application features, making it suitable for all kinds of application.

Providing the primitive tools needed to test arbitrary properties of a system remains a powerful idea. The disadvantage to this flexibility is that the burden of writing good test cases is placed upon the user, something which could be improved with a more sophisticated service discovery mechanism and more bundled plugins. This is an area which could be expected to improve through open source contributions. Additionally, I expect that test suites would evolve over time, much in the same way as traditional unit test suites, as more edge cases and problems in production are experienced.

@@

Conceptually, the main concern I have is the duplication of knowledge between actual application configuration and the test suite needed to verify it. The same could be argued for software unit testing, but it seems that with the rise in popularity of tools of a declarative nature such as Chef and Puppet, there should be a way to remove some of this duplication.

I hope that the concepts and implementation of this tool can be directly re-used and expanded upon in future by open source contributions or competing projects, I feel that there is still lots of room for improvement but believe that it can be realised in time with this approach.
